Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-18 Docs/Paper/LaTex/template.tex
general comments
Comments Fixed

\newcommand{\head}[1]{\textnormal{\textbf{#1}}}

@@

\begin{abstract}
\textcolor{blue}{Atualizar o abstract para descrever brevemente os novos algoritmos desenvolvidos}
We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing. The multi-core SMT-based BMC approach allows initializing many verification instances based on processors cores numbers available to the model checker. Each instance checks for a different optimum value until the optimization problem is satisfied. The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. We compare the experimental results of our proposed approach with Integer Linear Programming and the Genetic Algorithm.
\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
\end{abstract}

@@

\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.

@@

%----------------------------------------------
\subsection{Optimization}
%----------------------------------------------

Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9]. In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages. The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit. Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].

@@

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours running before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA [9]. The only drawback is that the found solution may not be the global minimum or maximum.

@@

\begin{lstlisting}
1. (declare-const K Int) 
2. (declare-const W Int)
3. (assert (< K 2)) 
4. (assert (< (- W K) 1))
5. (maximize (+ K W)) 
6. (check-sat)
\end{lstlisting}

@@

@@

\textcolor{Red}{As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals. This approach leads to a high impact in the verification time. However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
\begin{lstlisting}
01. GetNextStep(){
02.  int largestChunk = -1;
03.  chunk largest;
04.  for each(chunk in chunks){
05.     if(chunk.right - chunk.left > largestChunk){
06.           largestChunk = chunk.right - chunk.left;
07.           largest = chunk;
08.     }
09.   }	
10.   chunks.remove(largest);	
11.   int median = largest.left + floor((largest.right - largest.left) / 2)
12.   if(median > 0){
13.      if(largest.right - largest.left > 1)
14.         chunks.add(new chunk(largest.left, median - 1));	
15.      if(largest.right != largest.left)
16.         chunks.add(new chunk(median + 1, largest.right);
17.    }
18.   return median;
19. }
\end{lstlisting}
\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed. From line 4 to 9 the algorithm finds the biggest interval. Then from the line 10 the biggest interval is removed and the median is calculated in the line 11. Then 2 new intervals are created, the left side on line 14 and the right side on the line 16. At the end, the median is returned.}

\begin{lstlisting}
01. step = controller.GetNextStep();
02. int pid = ExecuteStep(step);
03. while(isRunning(pid)){
04.   if(!controller.isNeeded(step))
05.    kill(pid);
06. }     
\end{lstlisting}
\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances. The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2). While the step is being executed, the controller checks whether this step is still needed (line 4). If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}

@@

\begin{lstlisting}
01. Initialize Variables 
02. Declare number of nodes and edges
03. Declare hardware cost of each node as array (h)
04. Declare software cost of each node as array (s)
05. Declare communication cost of each edge (c)
06. Declare the initial software cost of (S0)
07. Declare transposed incidence matrix graph G (E)
08. Define the solutions variable (Xi) as Boolean
09. main {
10.  for TipH = 0 to Hmax do {
11.   populate Xi with nondeterministic/test values
12.   Calculate s(1-x)+c|Ex| and store at variable
13.   Requirement isured by Assume (Variable <= S0)
14.   Calculate Hp cost Based on value tested of Xi
15.   Violation check with Assert(Hp > TipH)
16.  }
17. }
\end{lstlisting}

@@

\begin{lstlisting}
01.#Init Values
02.  Create vZ context 
03.  Create binary vector (x)
04.  Declare number of nodes, edges and S0
05.  Declare hardware cost of each node as array (h) 
06.  Declare software cost of each node as array (s)
07.  Declare communication cost of each edge (c)
08.  Declare transposed incidence matrix graph G (E)
09.#Arithmetic
10.  SF receive s(1-x)
11.  TMP vector receive E|x| 
12.  CMC receive c*|EX|
13.  Fobj receive  x[i] * h[i]
14.#Asserts
15.  Add restrictions (SF + CMC <= S0)
16.  Add restrictions to minimize Fobj
17.  Check Model
18.  Print Result
\end{lstlisting}

@@

\textcolor{Green}{The vertices in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area.}  \textbf{Graphs nao deveria ser Tabela? acho que esse texto veio daquele artigo expandido. esse paragrafo faz sentido ao senhor? }

@@

@@

@@

@@

% end of file template.tex

>>>>

\newcommand{\head}[1]{\textnormal{\textbf{#1}}}
\renewcommand{\lstlistingname}{Algorithm}

@@

\begin{abstract}
\textcolor{blue}{Atualizar o abstract para descrever brevemente os novos algoritmos desenvolvidos}
We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing. The multi-core SMT-based BMC approach allows initializing many verification instances based on processors cores numbers available to the model checker. Each instance checks for a different optimum value until the optimization problem is satisfied. The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. \textcolor{Red}{O problema de particionamento de HW-SW foi modelo em diversas plataformas como: MATLAB R2013a da MathWorks[19], Z3 um solucionador de teoremas da Microsoft Research[32] e ESBMC utilizando abordagens single-core e multi-core. Os algoritmos implementados são discutidos e suas particularidades destacadas, por fim, faz-se um comparativos dos resultados obtidos. }
\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
\end{abstract}

@@

\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].}

\textcolor{Red}{O algoritmo ILP usa a intlinprog da biblioteca "Optimization Toolbox"[35], sua funcao é procurar o menor valor que satisfaca o problema descrito na Eq.(1). entretanto, para determinados tipos de problema ILP se torna inviavel dado o alto custo computacional, GA é uma forma de otimizar o tempo de processamento em detrimento da precisão, uma vez que GA não garante achar o valor máximo ou minimo para a problema. vZ usa funcoes de otimizacao e reescreve formulas em SMT para achar a solucao ideal, vZ apoia sua solucao em motores(OptSMT, MaxSMT).}

To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.

@@

\textcolor{red}{Optimization is the act of obtaining the best result (i.e., the optimal solution) under given circumstances [9]. In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages. The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit. Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function [9].}
%----------------------------------------------
\subsection{Optimization}
%----------------------------------------------

@@

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours belerunning before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, e.g., those used in the GA [9]. The only drawback is that the found solution may not be the global minimum or maximum.

\textcolor{red}{Ferramentas como vZ e ESBMC tambem exploram o problema de otimizacao, ambas ferramentas tem como principal finalidade a precisão na resposta, problemas com uma quantidade muito grande de dados torna o tempo um impecilho. as secoes 2.2 e 2.3 demonstram como vZ e ESBMC usam respectivamente suas tecnicas para resolucao dos problemas de particionamento, espera-se destas tecnicas uma resposta exata em um tempo razoavel.}

@@

\begin{lstlisting}[caption=Code "SMT" using vZ, label=vZ]
1. (declare-const K Int) 
2. (declare-const W Int)
3. (assert (< K 2)) 
4. (assert (< (- W K) 1))
5. (maximize (+ K W)) 
6. (check-sat)
\end{lstlisting}

@@

\textcolor{blue}{Introducao da secao.}

@@

\textcolor{Red}{As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals. This approach leads to a high impact in the verification time. However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}

\textcolor{blue}{Colocar um caption em todos os algoritmos.}

\begin{lstlisting}[caption=Calculate Steps and Chunks]
01. GetNextStep(){
02.  int largestChunk = -1;
03.  chunk largest;
04.  for each(chunk in chunks){
05.     if(chunk.right - chunk.left > largestChunk){
06.           largestChunk = chunk.right - chunk.left;
07.           largest = chunk;
08.     }
09.   }	
10.   chunks.remove(largest);	
11.   int median = largest.left + floor((largest.right - largest.left) / 2)
12.   if(median > 0){
13.      if(largest.right - largest.left > 1)
14.         chunks.add(new chunk(largest.left, median - 1));	
15.      if(largest.right != largest.left)
16.         chunks.add(new chunk(median + 1, largest.right);
17.    }
18.   return median;
19. }
\end{lstlisting}
\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed. From line 4 to 9 the algorithm finds the biggest interval. Then from the line 10 the biggest interval is removed and the median is calculated in the line 11. Then 2 new intervals are created, the left side on line 14 and the right side on the line 16. At the end, the median is returned.}

\textcolor{blue}{Colocar um caption em todos os algoritmos.}

\begin{lstlisting}[caption=Manager Controller]
01. step = controller.GetNextStep();
02. int pid = ExecuteStep(step);
03. while(isRunning(pid)){
04.   if(!controller.isNeeded(step))
05.    kill(pid);
06. }     
\end{lstlisting}
\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances. The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2). While the step is being executed, the controller checks whether this step is still needed (line 4). If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}

%----------------------------------------------
\section{Verification Algorithm using ESBMC}
%----------------------------------------------

@@

\textcolor{blue}{Colocar um caption em todos os algoritmos.}

\begin{lstlisting}[caption=Pseudocode describing ESBMC]
01. Initialize Variables 
02. Declare number of nodes and edges
03. Declare hardware cost of each node as array (h)
04. Declare software cost of each node as array (s)
05. Declare communication cost of each edge (c)
06. Declare the initial software cost of (S0)
07. Declare transposed incidence matrix graph G (E)
08. Define the solutions variable (Xi) as Boolean
09. main {
10.  for TipH = 0 to Hmax do {
11.   populate Xi with nondeterministic/test values
12.   Calculate s(1-x)+c|Ex| and store at variable
13.   Requirement isured by Assume (Variable <= S0)
14.   Calculate Hp cost Based on value tested of Xi
15.   Violation check with Assert(Hp > TipH)
16.  }
17. }
\end{lstlisting}

@@

\textcolor{blue}{Colocar um caption em todos os algoritmos.}

\begin{lstlisting}[caption=Pseudocode describing vZ]
01.#Init Values
02.  Create vZ context 
03.  Create binary vector (x)
04.  Declare number of nodes, edges and S0
05.  Declare hardware cost of each node as array (h) 
06.  Declare software cost of each node as array (s)
07.  Declare communication cost of each edge (c)
08.  Declare transposed incidence matrix graph G (E)
09.#Arithmetic
10.  SF receive s(1-x)
11.  TMP vector receive E|x| 
12.  CMC receive c*|EX|
13.  Fobj receive  x[i] * h[i]
14.#Asserts
15.  Add restrictions (SF + CMC <= S0)
16.  Add restrictions to minimize Fobj
17.  Check Model
18.  Print Result
\end{lstlisting}

@@

@@

\textcolor{Red}{A tabela 3 é uma extensão da tabela 2. A tabela 3 mostra problemas com uma quantidade maior de nós e arestas, este aumento impacta diretamente no tempo de processamento. RC6 obteve time out para todas as versões do ESBMC, vZ e GA não obtiveram resposta correta, e ILP resolveu corretamente o problema. Fuzzy teve 3 time outs, 3 memory outs, e uma resposta incorreta. ILP foi o unico que conseguiu resolver Mars, GA respondeu incorretamente e todos os outros algoritmos deram TO ou MO.  }

@@

\end{tabular}
\end{table}
\textcolor{Red}{Clustering descrito na tabela 2 parece ser o limiar para testar as ferramentas descritas, é importante destacar o numero de nós, fica evidente que nós superiores a 150 acarretam em TO,MO e respostas erradas por parte das ferramentas. ILP mostrou robustez ao conseguir resultados satisfatorios processando uma grande quantidade de nós e arestas.}

@@

\textcolor{blue}{Descrever mais dois ou três trabalhos relacionados, em especial, os artigos do vZ.}

@@

% end of file template.texe os
